---
title: "PopGenAnalysis"
author: "Jeffrey Chen"
date: "`r format(Sys.time(), '%d %b %Y')`"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: false
vignette: >
  %\VignetteIndexEntry{PopGenAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

`PopGenAnalysis` is an R package for is to view various different plots for different types of population genomic data such as PCA plots for data sets of populations with different numerical attributes for HWE plots, etc.

To download **PopGenAnalysis**:

``` r
require("devtools")
devtools::install_github("Heffley/PopGenAnalysis"，build_vignettes = TRUE)
library(PopGenAnalysis)
```

To list all functions available in this package:

```r
ls("package:PopGenAnalysis")
```

<br>

## Components
There are 3 functions in the package:

The __*pcaPopulationPlot*__ allows users to input the chromosome name and gene range as arguments, then returns the summary for all transcripts within the input range, with information of gene name, transcript 

The __*hwHeatPlot*__ function generates the plot heatmap showing significant departures from HWE where the pink values are where p are less than or equal to alpha.

The __*provestiDistDendo*__ will display a dendogram of random n individuals/populations #' to visualize  a genetic distance with a given data set.


<br>

```{r setup}
library(PopGenAnalysis)
```
